Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-12-05 paper/main.tex
more affil and funding updates

{ \red{personal funding sources}}
SJS acknowledges support from DOE grant DE-SC0009999 and NSF/AURA grant N56981C.
AIM acknowledges support from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the Federal Ministry of Education and Research.
During the completion of this work, AIM was advised by David W. Hogg and was supported by National Science Foundation grant AST-1517237.
JYHS acknowledges financial support from the MyBrainSc Scholarship (Ministry of Education, Malaysia), and the supervision of Ofer Lahav and Benjamin Joachimi.
JYHS would also like to thank Antonella Palmese and Boris Leistedt for guidance on the use of the algorithms ANNz2 and Delight respectively.
MB acknowledges support from the Agreement ASI/INAF 2018-23-HH.0 - Phase D.
AJC and JBK acknowledges support from DOE grant DE-SC-0011635. AJC, JBK, MLG, CBM acknowledge support from the DIRAC Institute in the Department of Astronomy at the University of Washington. The DIRAC Institute is supported through generous gifts from the Charles and Lisa Simonyi Fund for Arts and Sciences, and the Washington Research Foundation.
MJJ acknowledges support from Oxford Hintze Centre for Astrophysical Surveys which is funded through generous support from the Hintze Family Charitable Foundation.
CBM is supported in part by the National Science Foundation through Cooperative Agreement 1258333 managed by the Association of Universities for Research in Astronomy(AURA), and the Department of Energy under Contract No. DE-AC02-76SF00515 with the SLAC National Accelerator Laboratory. Additional LSST funding comes from private donations, grants to universities, and in-kind support from LSSTC Institutional Members.

>>>>

{ \red{personal funding sources}}
SJS and EN acknowledge support from DOE grant DE-SC0009999.  SJS acknowledges support from NSF/AURA grant N56981C.
AIM acknowledges support from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the Federal Ministry of Education and Research.
During the completion of this work, AIM was advised by David W. Hogg and was supported by National Science Foundation grant AST-1517237.
JYHS acknowledges financial support from the MyBrainSc Scholarship (Ministry of Education, Malaysia), and the supervision of Ofer Lahav and Benjamin Joachimi.
JYHS would also like to thank Antonella Palmese and Boris Leistedt for guidance on the use of the algorithms ANNz2 and Delight respectively.
MB acknowledges support from the Agreement ASI/INAF 2018-23-HH.0 - Phase D.
AJC and JBK acknowledges support from DOE grant DE-SC-0011635. AJC, JBK, MLG, CBM acknowledge support from the DIRAC Institute in the Department of Astronomy at the University of Washington. The DIRAC Institute is supported through generous gifts from the Charles and Lisa Simonyi Fund for Arts and Sciences, and the Washington Research Foundation.
MJJ acknowledges support from Oxford Hintze Centre for Astrophysical Surveys which is funded through generous support from the Hintze Family Charitable Foundation.
CBM is supported in part by the National Science Foundation through Cooperative Agreement 1258333 managed by the Association of Universities for Research in Astronomy(AURA), and the Department of Energy under Contract No. DE-AC02-76SF00515 with the SLAC National Accelerator Laboratory. Additional LSST funding comes from private donations, grants to universities, and in-kind support from LSSTC Institutional Members.
RI acknowledges support from FAPESP grant 2019/11321-9 and CNPq grant 306943/2017-4.
